Estimating real-time highstreet footfall from Wi-Fi probe requests

### 2018-06-24 paper/sections/methodology.tex
methodology figures progress

Data collection was done with the help of custom sensors built from modifing the Smart street sensor \citep{sss2016} hardware and updating them with custom software.
The sensor is essentially a Raspberry Pi connected with Wi-Fi and 3G antennae.
It keeps the Wi-Fi module in `Monitor' mode and uses the open source software - wireshark cite to passively collect all packets sent to `broadcast', marked with type - `management' and subtype - `probe requests'.
The MAC address in these probe requests is anonymised using a cryptographic hashing algorithm and transmitted through 3G connection to a central database via web-sockets protocol, where it is stored in a PostgreSQL database for further analysis.
A overall schematic of the data collection process is shown in Figure.
The ground truth on number of pedestrian footfall was recorded using a purpose built Android application cite.

@@

>>>>

Data collection was done with the help of custom sensors built from modifing the Smart street sensor \citep{sss2016} hardware and updating them with custom software.
The sensor is essentially a Raspberry Pi connected with Wi-Fi and 3G antennae.
It keeps the Wi-Fi module in `Monitor' mode and uses the open source software - wireshark cite to passively collect all packets sent to `broadcast', marked with type - `management' and subtype - `probe requests'.
The MAC address in these probe requests is anonymised using a cryptographic hashing algorithm and transmitted through 3G connection to a central database via web-sockets protocol, where it is stored in a PostgreSQL database for further analysis.
A overall schematic of the data collection process is shown in Figure \ref{datacollection_schematic}.
The ground truth on number of pedestrian footfall was recorded using a purpose built Android application cite.

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{images/datacollection_schematic.jpeg}
	\caption{Schematic diagram showing the process of collecting probe requests using the sensor} \label{datacollection_schematic}
\end{figure}

@@

\begin{figure}
	\centering
	\subfigure[]{
	\resizebox*{0.48\linewidth}{!}{\includegraphics{images/pilot_counts_comparision.png}}}
	\subfigure[]{
	\resizebox*{0.48\linewidth}{!}{\includegraphics{images/pilot_counts_comparision.png}}}
	\caption{Schematic diagrams explaining the methods for filtering by signal strength and clustering using sequence numbers} \label{sample-figure}
\end{figure}
